\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-10 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\subsection{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent %This is a very important point, and we thank the referee for raising it.
The referee definitely raised a very important point here, and indeed, Census data do report the quantity of goods (and sometimes even two quantities).
%At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities?
In this context, the findings in \cite{Lashkaripour_JIE2020} are specifically enlightening.
Based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and the cost of transportation increases more rapidly with unit weight than the cost of production. \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the iceberg cost assumption regarding transport costs.
This result of transport costs close to be totally iceberg contrasts from our own findings of additive costs representing 30 to 45\% of total costs. Some elements can yet be put forward to account for the difference of results. Beyond a longer time span, our database is exhaustive, and encompasses all goods and industries, while \citet{Lashkaripour_JIE2020}) restricts to indivisible/discrete goods that represent a bit more 56\% of US total imports of goods in his dataset. In this regard, when comparing Tables 1 and 10 in \citet{Lashkaripour_JIE2020}, one can see that the share of multiplicative costs tends to decrease with the share of discrete goods. It is therefore reasonable to think that the inclusion of all goods, like in our setting, would move the average share of multiplicative costs away from 100\%.

Nevertheless, considering the importance of the referee's remark, we went beyond this very first argument to investigate this question in depth. This was not without difficulty yet, in particular due to data and estimation constraints. At a more fundamental level, we also believe that looking at transport costs on a per-weight basis does add relevant information. We develop each line of argument in what follows.

@@

%The two stories are not necessarily incompatible, however.

%Nevertheless, the point made by the referee is an important one and deserves careful investigation. We devoted a lot of thought to a potential switch from weight to quantity.
%Running the estimation considering quantities (i.e., units) rather than weight, still on the transport mode-yearly basis yet appears really uneasy in our context for several, non-trivial reasons, that we develop below.

\subsubsection{Data availability issue}

In our attempt to address the referee's remark, we faced a first difficulty regarding the availability of information on quantities. Neither the US Bureau of Census data nor the 1974-2004 Hummels's data (based on the Census Bureau data) do report the quantity by transport mode. This is incompatible with our empirical strategy of estimation transport costs which is conditional on the transport mode, similarly as in \cite{hummels2007}. As a result, computing the unit price of all trade would require the assumption that the weight per unit is the same for vessel shipments and air shipments at the level of the observation. This is unlikely, as one would expect the higher-to-weight value to be transported by air rather than by vessel. The alternative would then be to only consider single-mode flows. In Hummels's data (1974-2014), on average 41.1 \% of trade flows and 79\% of trade value are multi-mode. This would reduce the total value of the sample from 12,500 billion dollars to 2,650 billion dollars, entailing a large loss of useful information. Original census data, when accessible (from 2002 because of the Covid situation), are more promising.\footnote{Original Census data are  reported at the HS-10 digit $\times$ district of entry $\times$ district of unleading $\times$ rate provision code.} In 2019, multi-modal flows are 570 billion dollars out of 1,790 billion dollars, or 31\% of the data. This is still a large share, but not too large to preclude any work. Accordingly, we dig deeper into this issue with the US Census dataset starting in 2002, restricted to single transport mode flows. \smallskip

@@

The second difficulty dwells on the units used to measure quantities. The Census data, if it provides some information on quantity, remains silent on the units considered. To the best of our knowledge, these can only be found in the ``Harmonized Tariff Schedule of the United State''. Unfortunately, these schedules change many time per year and only the schedules from 2009 onwards were available in a .csv format. On the years for which the match could be done (from 2009), it turns out that at our sector level (3-digit), goods (either at the 5-digit or the 10-digit level) are measured in different units. In 2019, only 125 3-digit sectors out of 230 are measured in a single unit (after cleaning up the unit names\footnote{As units are not always coherent (eg weight can be given in ``kg’’, ``kg.'' ``Kg'' and, also, ``g'' and ``t'').}).\footnote{For instance, 3-digit SITC sector ``061 Sugar, molasses and honey'' includes among other products, 5-digit SITC product ``6150 Molasses, whether or not decolourized'', measured in liters and 5-digit SITC product ``06160 Natural Honey'' measured in kg. Actually worse than this, the 5-digit SITC product ``06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel'' includes both 10-digit HTS product ``1702903500 Other: invert molasses'', measured in liters and 10-digit HTS product ``1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions''  measured in kilograms.} Neglecting these differences would invalidate our functional forms, as no one expects the transport cost of a ``piece'' to be the same as the transport cost of a ``kg'', even in the same sector.
So we are limited to using quantity units from 2009 to 2019, amending our structure of fixed effects to consider the triplet (origin country, sector, quantity unit).

\subsubsection{Estimation issue}

Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight prices. As discussed above, in our baseline regression we separate each transport cost component in its two distinct sector-origin country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could indeed be easily replaced by (sector, quantity unit) fixed effects; but the same does not appear relevant for country fixed effects. Let us elaborate on this issue.

In the per-weight price, the existence of a single country fixed effect applicable to all sectors could be justified, as a kilogram is always a kilogram and one can assume they both add the same to transport from, say, Germany. In contrast, an unit of tee-shirt is quite different from an unit of car. To clarify this point, assume imports of tee-shirts and cars from Germany and China. Under the separability assumption, importing a tee-shirt from either country implies paying the fixed effect for both countries (the same for all sectors) and the fixed effect for the sector (the same for all countries); and similarly for importing a car. Hence, the difference in the cost of importing a car from Germany versus China would be the same, in dollars, as the difference between the cost of importing a tee-shirt from Germany relative to China. This does not seem a sensible assumption; in this case specifically, we cannot keep the separability assumption.
As discussed before, this dramatically increases the computational difficulty of our method (with no substantial different results, see Subsection 3.3.1. in the main paper).\smallskip

@@

Integrating these various constraints, we run the robustness check (weight versus quantity) \textit{i)} on a sample reduced over 2009-2019, considering single transport mode flows - amounting to 66\% of the value of the baseline sample; \textit{ii)} retaining a non-separable structure of three-dimensional fixed effects $t_{is(k)u}$, $\tau_{is(k)u}$ according to the following equation:
\begin{equation*}
\ln\left(\frac{p_{iku}}{\widetilde{p}_{iku}}-1 \right)= \ln \left(\tau_{is(k)u} -1+\frac{t_{is(k)u} }{\widetilde{p}_{iku}} \right) + \epsilon_{iku}
\end{equation*}
\noindent where $p_{iku}$ refers to the cif price associated with quantity of goof $k$ imported from country $i$, measured in unit $u$, $\widetilde{p}_{iku}$ the corresponding unit value (fas price). Depending on the sector, two different units are considered, kilograms and numbers.

The results are reported in Table \ref{tab_comp_wgt_qty} and in Figure \ref{graph_comp_wgt_qty} (as well as in the online appendix D.4. In Table \ref{tab_comp_wgt_qty}, for each transport mode, the first column reports the estimation based on the price per quantity; while the second column reports the results obtained considering the price per kg on the same sample; the last column reported our baseline results on the large sample (considering the average value over 2005-2019, under the separability assumption).

@@

\begin{table}[htbp]
	\caption{Comparison: Price per quantity versus per kg, 2009-2019}
	\begin{center}		
		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy_reshaped.tex}
%		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy.tex}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
			\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
		\end{tabular}
	\end{center}
		\label{graph_comp_wgt_qty}%
\end{figure}

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions that strongly limit both the number of sectors and of countries covered, do also impact the value of trade flows covered. In our view, this raises a non-trivial sample selection bias that may reduce the general scope of the transport cost estimates. Second, in terms of $\beta$ estimates, the results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air). In this regard, they stand in line with the results of \cite{Lashkaripour_JIE2020}, stressing the correlation between weight per unit and unit price. Still, the share of additive cost is not reduced to zero (except if one looks at the median for vessel). Thus these results do not disqualify our approach, especially as we cover a much larger period and sample with our baseline estimate.

@@

\subsubsection{On the relevance of the price per-weight approach}
At a more fundamental level, we do believe that the study of transport costs measured on a per-weight price add some relevant information on the international transport cost burden faced by exporters. Let us explain the underlying rationale.

Our main objective in this paper is to provide a quantitative assessment of the international transport costs burden over time; on that matter, one may start with the observation that transport cost schedules are expressed through a mixed, per-weight and per-volume basis, both historically and nowadays. For example, in 2021, air freight trade costs are expressed in weights, with a minimal weight per volume (``volumetric weight'' or ``dimensional weight'')\footnote{See for example \href{https://transporteca.co.uk/shipping-costs}{https://transporteca.co.uk/shipping-costs}, \href{http://wap.dhl.com/serv/volweight.html}{http://wap.dhl.com/serv/volweight.html} and \href{https://en.wikipedia.org/wiki/Dimensional_weight}{ https://en.wikipedia.org/wiki/Dimensional\_weight}).} while maritime freight costs are expressed in volume.
Hence, looking at per-kg transport cost can be interpreted straightforwardly as trying to estimate the actual existing shipping costs, with sector fixed effects interpretable as measure of mean density for different sectors. The existence of per-volume or per-weight shipping cost is directly linked to the technical constraints of the transportation sector, hence exogenous to exporting firms' decisions. In contrast, per-unit shipping cost depends on the behavior of exporting firms. The shipping cost per weight is one of the exogenous parameters firms take into account in their production choices, including weight per unit. Accordingly, studying the technical per-volume or per-weight shipping cost is interesting to understand the context in which they operate.

@@

Another argument is illustrated by Figure \ref{graph_Share_of_discrete_goods.png}. After computing the share of discrete goods per 5-digit SITC import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports on a yearly basis. According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, reaching a value only above 50\% for two years. Switching to a per-unit approach would hence mean a marked reduction in the trade flows coverage, thereby limiting the general scope of our estimates.

\begin{figure}[htbp]
	\caption{Estimated share of discrete goods in US imports, 1974-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/Share_of_discrete_goods.png}\\
		\end{tabular}
	\end{center}
	\label{graph_Share_of_discrete_goods.png}%
\end{figure}

After considering all the above arguments in depth, we decided not to switch the paper from the study of price per weight to the study of price per quantity. We thus maintained our original empirical strategy covering the whole period 1974-2019 in the revised version, while we extended the online Appendix with this supplementary robustness check. We hope to have convinced you that this is a relevant choice.

### 2021-11-10 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Requête
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
nouvelle tentative
Travail Guillaume - Lise sur le modèle
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{figure}[htbp]
\caption{Share of additive costs $\beta$ (3-digit classification)}
\label{fig:part_cout_additif}
\begin{center}
 \includegraphics[width=12cm, height=7.5cm]{Figure1_share_of_additive_in_totalTC.jpg}
%{\footnotesize {OECD data} }
\begin{minipage} [c]  {5in} \scriptsize%
Notes:The share of additive costs $\beta$ is reported on the $y-$axis. Each yearly value is obtained as: $\frac{\frac{\widehat{t}}{\widetilde{p}}}{\widehat{\tau}-1+\frac{\widehat{t}}{\widetilde{p}}}$, expressed in percent of the export price $\widetilde{p}$ (at the 3-digit level).
\end{minipage}
\end{center}
\end{figure}

@@

In this section, we explore the implications of our empirical results on theoretical grounds. Over the last decade, several papers examined the implications of additive/per-shipment costs. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. We complement these various outcome by providing a long-run characterization of both additive and multiplicative component of transports costs. Second, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction is achieved through a combined reduction in the ad-valorem and the additive components (as quantified by our empirical model) or solely through the ad-valorem cost (as standardly modelled in New Trade theoretical approaches). To this aim, we embed additive costs in the canonical \citet{melitz} model.\smallskip
%While the bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation.

\cite{Irrazabal_2015}, \cite{sorensen2014} and \cite{Lashkaripour_JIE2020} have preceded us on this issue. We differentiate from them in the following way. \cite{sorensen2014} explores the welfare effects of a trade costs reduction depending on whether they are either fully ad-valorem or fully additive on analytical grounds. In contrast, we provide a quantification of such welfare gains, as in \cite{Irrazabal_2015} or \cite{Lashkaripour_JIE2020}. In a partial-equilibrium model with perfect competition, \cite{Lashkaripour_JIE2020} obtains that welfare gains are not substantially different whether the transport cost decrease implies an additive component or not. This stands in contrast with the conclusion reached by \cite{sorensen2014} (analytically) and \cite{Irrazabal_2015} (quantitatively) in M\'{e}litz' type models. We also find (see below) the transport cost reduction implies substantially larger welfare gains when they are achieved through a reduction in the additive component.

That said, it should be noted the case with additive costs in \cites{Lashkaripour_JIE2020}paper relies on a negligible share of additive costs. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} relies on a perfectly competitive environment, we use a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}, as did \cite{sorensen2014} and \cite{Irrazabal_2015}. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.

@@

We rely on the model developed by \cite{sorensen2014}, which amends the two-country model of \cite{melitz} with monopolistic competition and endogenous firm entry to include additive costs.\footnote{\cite{Irrazabal_2015} adopt the multi-country model of \cite{chaney2008}, consistently with their database that documents the exports of Norwegian firms in various destination markets worldwide. We rather choose to retain the \cite{melitz} model, in its simplest form with one sector and two symmetric countries, picking up the average estimated values of transport costs based on our unique importer country, e.g. the US. Sticking to this canonical set-up allows us to illustrate the role of additive costs in a transparent and intuitive way.} Since our focus in on the role of additive versus ad-valorem transport costs, we directly present the two-country version of the model, with the two countries (Home and Foreign) being perfectly symmetric. For the sake of space, we only present here the building blocks of the model. More details can be found in Appendix \ref{app:theoretical_model}.

@@

In each country, the representative household exogenously supplies $L$ units of labour and maximizes utility $\mathcal{U} = \left[ \int_{\omega \in \Omega}c(\omega)^{\frac{\sigma-1}{\sigma}} d\omega \right]^{\frac{\sigma}{\sigma-1}}$, with $\sigma>1$ the elasticity of substitution between varieties $\omega$. She chooses her consumption $c(\omega)$  within the set $\Omega$ of available varieties (made of both domestic and foreign varieties, endogenously defined), subject to her budget constraint: $\int_{\omega \in \Omega} p(\omega) c(\omega) dw \leq E$, with $p(\omega)$ the consumer price of variety $\omega$ and $E$ nominal expenditures. As standard, the optimal demand function for variety $\omega$ is: $c(\omega) = \left(\frac{p(\omega)}{P}  \right)^{-\sigma} \frac{E}{P}$ with the associated optimal price index $P$ equal to $P = \left[ \int_{\omega \in \Omega}p(\omega)^{1-\sigma}d\omega\right]^{\frac{1}{1-\sigma}} $.

\subsubsection{Firms behavior}

As in \cite{melitz}, firms are in monopolistic competition, each producing a differentiated variety using labor as sole production factor. Both countries being perfectly symmetric, the labor market equilibrium imposes the same wage in both countries, thus considered as the num\'{e}raire. Prices and costs are hence expressed in terms of labor. At entry, each firm pays a sunk entry cost $f_e$ and subsequently draws its productivity level $\varphi$ from a known distribution $G(\varphi)$. The production of $q$ units requires employing $l(q|\varphi) = f+\frac{q}{\varphi}$ units of labor, with $f$ the fixed cost of production. Exporting is subject to an extra fixed cost $f_x$ and variable exporting costs of two types: an ad-valorem cost that depends on the value traded $\tau\geq 1$ (as in \citealp{melitz}) and an additive cost depending on the quantity (weight) transported, $t\geq 0$ - not included in the canonical Melitz model. At each point in time, a firm can be hit by a death shock at the exogenous probability $\delta>0$. Following \cite{melitz}, we solve the problem backwards. First, we solve for the maximizing profit behavior once entered. Second, we determine the entry conditions on both the domestic and the export markets.\medskip

\paragraph{Profit-maximizing behaviors} Once entered, and conditional on being able to export, a firm adopts a pricing-to-market behavior by setting a specific price on each destination market. For each destination market, the firm sets a constant markup on its marginal cost, which is a decreasing function of the firm's productivity $\varphi$, but also takes into account both components of trade costs on the export market, according to:
\begin{eqnarray}
p_d(\varphi) &=& \frac{\sigma}{\sigma-1}\frac{1}{\varphi} \notag \\
p_x(\varphi) &=& \frac{\sigma}{\sigma-1}\left[\frac{\tau}{\varphi} +t \right] \label{eq:px}
\end{eqnarray}

Under the assumption of symmetric countries (i.e, implying $E=E^\ast$ and $P=P^\ast$), one can deduce the profits on the domestic and export markets ($\pi_d(\varphi)$ and $\pi_x(\varphi)$) respectively as:
\begin{eqnarray}
\pi_d(\varphi)  &=& \frac{r_d(\varphi)}{\sigma} - f = B \varphi^{\sigma-1} - f \label{eq:pid_rd}\\
\pi_x(\varphi) &=& \frac{r_x(\varphi)}{\sigma} - f_x = B \left[ \frac{\tau}{\varphi} + t\right]^{-(\sigma-1)} - f_x \label{eq:pix_rx}
\end{eqnarray}
\noindent with $B \equiv \frac{1}{\sigma-1}\left(\frac{\sigma}{\sigma-1}\right)^{-\sigma}P^{\sigma-1}E$ and where $r_d(\varphi)$ and $r_x(\varphi)$ denote the sales revenues on each market (see Appendix \ref{app:theoretical_model} for a detailed expression). Profits increase with productivity $\varphi$, and only sufficiently productive firms are able to cover the fixed costs of operating in a given market. Further, in presence of trade costs, a given firm of productivity $\varphi$ makes a lower export profit than on its domestic market, conditional on being productive enough to export. This drives us to determine the productivity threshold associated to the entry conditions.

\paragraph{Zero-cutoff profit conditions} Given the fixed costs on both the domestic and the export markets, only firms with a productivity above $\varphi^\ast$ will serve the domestic market, and those with $\varphi>\varphi_x^\ast$ will export abroad.  The two productivity thresholds can be linked according to:
\begin{equation}
\frac{\varphi_x^\ast}{\tau+t\varphi_x^\ast} = \varphi^\ast \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} \label{eq:link_thresholds}
\end{equation}

Following \cite{melitz} and the subsequent literature, we ensure selection on the export market, i.e. such that $\varphi_x^\ast > \varphi^\ast$. Making use of Equation (\ref{eq:link_thresholds}), this condition writes down as $\left[\tau+ t\varphi^\ast_x \right] \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} >1$. Due to additive costs ($t>0$), the export selection condition depends on the general equilibrium of the model (through $\varphi^\ast_x $) and cannot be imposed ex-ante by an appropriate restriction on the space parameter. We check this condition holds numerically when solving the model.\footnote{This is no longer the case under ad-valorem costs only. In this case, with $t=0$, we find the usual condition that $\varphi^\ast_x >\varphi^\ast$ iif $\tau^{\sigma-1}\frac{f_x}{f}>1$.}

@@

Following a standard assumption in this literature (\cite{Irrazabal_2015}, \cite{melitz-redding-Handbk-IT-2014}), the heterogeneity in firm productivity is assumed to be given by a Pareto distribution. As shown in \cite{melitz-redding-Handbk-IT-2014}, the Pareto distribution indeed allows for a full analytical solving of the M\'{e}litz model. This is no longer the case in the presence of additive costs (see Appendix \ref{app:theoretical_model}). In this case, we need to rely on the model's simulations to determine the steady state. This drives us to calibrate the structural parameters of the model. To do so, we dwell on values commonly retained in the literature, as reported in Table \ref{tab:calib_horsTC}.

>>>>

\begin{figure}[htbp]
\caption{Share of additive costs $\beta$ (3-digit classification)}
\label{fig:part_cout_additif}
\begin{center}
 \includegraphics[width=12cm, height=7.5cm]{Figure1_share_of_additive_in_totalTC.jpg}
%{\footnotesize {OECD data} }
\begin{minipage} [c]  {5in} \scriptsize%
Note:The share of additive costs $\beta$ is reported on the $y-$axis. Each yearly value is obtained as: $\frac{\frac{\widehat{t}}{\widetilde{p}}}{\widehat{\tau}-1+\frac{\widehat{t}}{\widetilde{p}}}$, expressed in percent of the export price $\widetilde{p}$ (at the 3-digit level).
\end{minipage}
\end{center}
\end{figure}

@@

In this section, we explore the implications of our empirical results on theoretical grounds. Over the last decade, several papers examined the implications of non-iceberg costs. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment, and draw welfare conclusions regarding the variations of these costs. We have complemented these studies by providing a long-run characterization of both the additive and the multiplicative component of transports costs. In this section, we use our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two measures. One measure assumes that the reduction was achieved solely through the decline of ad-valorem costs, as modeled in standard New Trade theoretical approaches. The other measures builds on the results of our empirical investigation to assume that the reduction was achieved by a combined reduction in the ad-valorem and the additive components, as modeled by the addition of additive costs to the canonical \citet{melitz} model.\smallskip
%While the bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation.

Our aim is related to \cite{Irrazabal_2015}, \cite{sorensen2014} and \cite{Lashkaripour_JIE2020}. We proceed in a different way. \cite{sorensen2014} explores the welfare effects of a trade costs reduction depending on whether they are either fully ad-valorem or fully additive on analytical grounds. In contrast, as in \cite{Irrazabal_2015}, we provide a quantification of such welfare gains. \cite{Irrazabal_2015}, though, does not look into the effect of the reduction of trade costs it provides estimates of transport costs only for one year. We ground our study in the observed reduction of transport costs from 1974 to 2019.  \cite{Lashkaripour_JIE2020} uses a partial-equilibrium model with perfect competition and builds on its result that for  denumerable goods, per-unit additive transport costs are very small to find a very small welfare effect of additive costs. We look at the whole range of goods over a longer period and use a \citet{melitz} model like \cite{sorensen2014} and \cite{Irrazabal_2015}. In that context,
%\cite{Lashkaripour_JIE2020} obtains that welfare gains are not substantially different whether the transport cost decrease implies an additive component or not. This stands in contrast with the conclusion reached by \cite{sorensen2014} (analytically) and \cite{Irrazabal_2015} (quantitatively) in M\'{e}litz's type models.
we find (see below) the transport cost reduction implies substantially larger welfare gains when they are achieved through a reduction in the additive component.

%That said, it should be noted the case with additive costs in \cites{Lashkaripour_JIE2020}paper relies on a negligible share of additive costs. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} relies on a perfectly competitive environment,
Using a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}, as did \cite{sorensen2014} and \cite{Irrazabal_2015} makes a difference. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Leaving aside the selection issue leads to an underestimation of the welfare gains that can be achieved by a reduction in additive transport costs.

@@

We rely on the model developed by \cite{sorensen2014}, which amends the two-country model of \cite{melitz} with monopolistic competition and endogenous firm entry to include additive costs.\footnote{\cite{Irrazabal_2015} adopt the multi-country model of \cite{chaney2008}.
%, consistently with their database that documents the exports of Norwegian firms in various destination markets worldwide.
We choose to retain the \cite{melitz} model, in its simplest form with one sector and two symmetric countries.
%, picking up the average estimated values of transport costs based on our unique importer country, e.g. the US.
Sticking to this canonical set-up allows us to illustrate the role of additive costs in a transparent and intuitive way.}
%Since our focus in on the role of additive versus ad-valorem transport costs, we directly present the two-country version of the model, with the two countries (Home and Foreign) being perfectly symmetric.
For the sake of space, we  present here only the building blocks of the model. More details can be found in Appendix \ref{app:theoretical_model}.

@@

In each country, the representative household exogenously supplies $L$ units of labour and maximizes utility $\mathcal{U} = \left[ \int_{\omega \in \Omega}c(\omega)^{\frac{\sigma-1}{\sigma}} d\omega \right]^{\frac{\sigma}{\sigma-1}}$, with $\sigma>1$ the elasticity of substitution between varieties $\omega$. She chooses her consumption $c(\omega)$  within the set $\Omega$ of available varieties (both domestic and foreign), subject to her budget constraint: $\int_{\omega \in \Omega} p(\omega) c(\omega) dw \leq E$, with $p(\omega)$ the consumer price of variety $\omega$ and $E$ nominal expenditures. The optimal demand function for variety $\omega$ is: $c(\omega) = \left(\frac{p(\omega)}{P}  \right)^{-\sigma} \frac{E}{P}$ with the associated optimal price index $P$ equal to $P = \left[ \int_{\omega \in \Omega}p(\omega)^{1-\sigma}d\omega\right]^{\frac{1}{1-\sigma}} $.

As in \cite{melitz}, firms are in monopolistic competition, each producing a differentiated variety using labor as sole production factor. Both countries are perfectly symmetric, the labor market equilibria impose an unique international wage that we use as the num\'{e}raire. At entry, each firm pays a sunk entry cost $f_e$ and subsequently draws its productivity level $\varphi$ from a known distribution $G(\varphi)$.  At each point in time, a firm can be terminated
%be hit by a death shock
at the exogenous probability $\delta>0$.
The production of $q$ units requires employing $l(q|\varphi) = f+\frac{q}{\varphi}$, units of labor, with $f$ the fixed cost of production. Exporting is subject to an extra fixed cost $f_x$ and variable exporting costs of two types: an ad-valorem cost that depends on the value traded $\tau\geq 1$ (as in \citealp{melitz}) and an additive cost depending on the quantity (weight) transported, $t\geq 0$. This $t$ is our innovation compared to the canonical Mélitz model.

Following \cite{melitz}, we solve the program of firms backwards. First, we solve for the maximizing profit behavior after entry. Second, we determine the entry conditions on both domestic and exporting markets.\medskip
\paragraph{Profit-maximizing behaviors} After entry, and conditional on being able to export, firms set a specific price on each destination market. The firm sets a constant markup on its marginal cost, which is a decreasing function of the firm's productivity $\varphi$, but also takes into account both components of trade costs on the destination market (see  Appendix \ref{app:theoretical_model}):
\begin{eqnarray}
p_d(\varphi) &=& \frac{\sigma}{\sigma-1}\frac{1}{\varphi} \notag \\
p_x(\varphi) &=& \frac{\sigma}{\sigma-1}\left[\frac{\tau}{\varphi} +t \right] \label{eq:px}
\end{eqnarray}

Under the assumption of symmetric countries (implying $E=E^\ast$ and $P=P^\ast$), one can compute the profits on the domestic and export markets ($\pi_d(\varphi)$ and $\pi_x(\varphi)$) respectively as:
\begin{eqnarray}
\pi_d(\varphi)  &=& \frac{r_d(\varphi)}{\sigma} - f = B \varphi^{\sigma-1} - f \label{eq:pid_rd}\\
\pi_x(\varphi) &=& \frac{r_x(\varphi)}{\sigma} - f_x = B \left[ \frac{\tau}{\varphi} + t\right]^{-(\sigma-1)} - f_x \label{eq:pix_rx}
\end{eqnarray}
\noindent $r_d(\varphi)$ and $r_x(\varphi)$ are the sales revenues on each market (see Appendix \ref{app:theoretical_model} for a detailed expression). $B \equiv \frac{1}{\sigma-1}\left(\frac{\sigma}{\sigma-1}\right)^{-\sigma}P^{\sigma-1}E$ . Profits increase with productivity $\varphi$.Only sufficiently productive firms are able to cover the fixed costs of operating in a given market. Further, in presence of trade costs, profits for a given productivity are lower on the export market than on the domestic market.
%a given firm of productivity $\varphi$ makes a lower export profit than on its domestic market, conditional on being productive enough to export.
We now determine the productivity threshold associated to the entry conditions.

\paragraph{Zero-cutoff profit conditions} Given the fixed costs on both the domestic and the export markets, only firms with a productivity above $\varphi^\ast$ will serve the domestic market, and only firms with a productivity above $\varphi_x^\ast$ will export. The two productivity thresholds can be linked according to:
\begin{equation}
\frac{\varphi_x^\ast}{\tau+t\varphi_x^\ast} = \varphi^\ast \left( \frac{f_x}{f} \right)^{\frac{1}{\sigma-1}} \label{eq:link_thresholds}
\end{equation}

Following \cite{melitz} and the subsequent literature, we impose selection on the export market, (i.e. $\varphi_x^\ast > \varphi^\ast$). From Equation (\ref{eq:link_thresholds}), this condition writes down as $\left[\tau+ t\varphi^\ast_x \right] \left( \frac{f_x}{f} \right)^{\frac{1}{\sigma-1}} >1$. In contrast to the ad-valorem only case, due to additive costs ($t>0$), the export selection condition depends on the equilibrium of the model (through $\varphi^\ast_x $) and cannot be imposed ex-ante by an appropriate restriction on parameters. We check this condition holds numerically when solving the model.
%\footnote{This is no longer the case under ad-valorem costs only. In this case, with $t=0$, we find the usual condition that $\varphi^\ast_x >\varphi^\ast$ iif $\tau^{\sigma-1}\frac{f_x}{f}>1$.}

@@

Following a standard assumption in this literature (\cite{Irrazabal_2015}, \cite{melitz-redding-Handbk-IT-2014}), the distribution in firm productivity is assumed to follow a Pareto distribution with parameters $(\varphi_{min},k)$. This allows a full analytical solving of the M\'{e}litz model. This is no longer the case in the presence of additive costs (see Appendix \ref{app:theoretical_model}). In this case, we need to rely on the model's simulations to determine the steady state. This drives us to calibrate the structural parameters of the model. To do so, we usevalues commonly retained in the literature, as reported in Table \ref{tab:calib_horsTC}.

\begin{table}[htb]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{13cm}{ \vspace{4pt}\footnotesize{Notes: $f$ is endogenously revealed such that all firms produce in autarky. $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (21\%, based on early 1980s value) and the final steady state (39\%, based on 2006 value), according to the references provided above.}}}
\end{table}
